\documentclass[10pt,english]{article}	

\usepackage[document]{ragged2e}

\usepackage{../../preamble}
\usepackage{../../customs}

\begin{document}

\columnratio{0.31}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}
\colseprulecolor{white}


% LEBENSLAUF HIERE
\AtBeginShipoutFirst{\Header{Cover Letter}\Footer{1}}
\AtBeginShipout{\AtBeginShipoutAddToBox{\Header{Cover Letter}\Footer{2}}}

\newpage

\colseprulecolor{lightcol}
\columnratio{0.67}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}

% \fcolorbox{white}{white}{
\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\LARGE{\textbf{\textcolor{maincol}{En-Liang (Leon) Lee}}} \\[2pt]
	\normalsize\icontext{MobilePhone}{16}{+44 7392 381253}{black}\\
	\iconemail{Envelope}{16}{enliang.leon.lee@gmail.com}{black}\\
\end{minipage}

\bigskip

\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\today
	\bigskip

	The Royal Lyceum Theatre Company

	30b Grindlay St

	EH3 9AX

	Edinburgh 

	GB
\end{minipage}
\bigskip\bigskip

Dear Sir or Madam,
\medskip

I am writing this cover letter to express my interest in applying to be Depute Head of Lighting of the Edinburgh Lyceum. As a previous Technical Manager of the Bedlam Theatre, and someone with a strong love of technical theatre, I believe that have the skills to prove myself useful along with the relevant passion and experience to assist running the venue.

\medskip

I have multiple years of technical theatre experience, and while attending my studies at the University of Edinburgh, I have been consistently active for the past 3 years at the University's student run theatre, the Bedlam as part of the EUTC (Edinburgh University Theatre Company). There I took part in over 25 shows, and have been Lighting Designer or Technical Manager of over 10. Additionally, in my final year I was part of the EUTC's 2024 - 205 Committee, acting as one of the Technical Managers, and over the past year have committed in helping teach safe practices and technical skills to younger students, helping in maintenance of the equipment, as well as making tech improvements around the buildling and planning of future technical upgrades. From this, I believe that I can match the experience and commitment it takes for this role. 

\medskip

In addition to being part of the EUTC during the semesters of my degree, I have also worked at the Edinburgh Fringe as a venue technician for 4 years, notably working as the Technical Manager of Bedlam Fringe 2025. From this role, I have developed good interpersonal skills, as I was partially responsible for communication with the 23 shows performing at the theatre as the primary contact to show teams for technical requirements in pre-production, as well as managing the Theatre during the festival alongside 3 other venue technicians showing my leadership and teamwork abilities. Communication within the management team was also important for the festival to run smoothly, and I kept in good contact with the Venue Manager, Programmer, and Front of House Manager all throughout the Fringe to ensure there were no problems. 

\medskip
In these roles working as techician, I have gained lots of experience in Lighting Design, as well as other aspects of technician work such as rigging, patching, programming, and operating, as well as projection. I have a lot of experience with various LX desks, including Zero88, Chamsys, and Avolites systems but particularly, I have lots of experience with using ETC desks and the Nomad. Notably, for the Fringe 2025, I made a base show file with a custom Augment3d file, and an extensive magic sheet for companies to pre-program their shows onto. I also have studied a lot into the creation of 3d building plans and rig plans via the software Vectorworks 2025, and I created a model of Bedlam Theatre Vectorworks file from a basic floor plan and manual measurements, which is now used in the theatre today.

\medskip

I hope my experience would be valuable, and thank you for looking at my application. I look forward to hearing from you.

\medskip
Sincerely,

Leon Lee.
\end{document}
