\documentclass[../../cv-cs.tex]{subfiles}
\begin{document}

% \cvlinkevent
% {\href{https:www.github.com/leon0241/nvim-leon}{Github Link}}
% {Custom Neovim Installation}
% {\begin{itemize}
% 	\item Created a custom Neovim installation from a barebones repository and implemented any necessary aspects of an IDE with open-source packages, such as language support, autocomplete, debugging, and a comprehensive snippet system.
% \end{itemize}}
%
\cvlinkevent
{\href{https:www.github.com/leon0241/leon-latex-thmboxes}{Package Link} | \href{https:www.github.com/leon0241/leon-latex-notes}{Notes Link}}
{LaTeX Notes System}
{
    \begin{itemize}
	\item Built a custom package using the tcolorbox and mdframed LaTeX packages, which creates compact and customisable theorem boxes for use in LaTeX documents.
	\item Using this package, I created an open course repository containing sets of notes for 11 courses I took throughout my degree for use in exams and revision.
    \end{itemize}
}

\cvlinkevent
{}
{Homelab Server}
{
    \begin{itemize}
	\item Built a custom Homelab server from an old desktop PC using Proxmox, running Debian images. I host an OpenMediaVault file server, Plex server, and adblocking through Pi-hole, as well as remote access to the server via Tailscale..
	\item Configured a dashboard by using prometheus-pve-exporter, Prometheus, and a Grafana front-end.
    \end{itemize}
}

\cvlinkevent
{}
{Personal Arch Linux setup}
{
    \begin{itemize}
	\item Configured a laptop which dual boots Windows 10 alongside Arch Linux running Hyprland, which I use as a daily driver. Created configuration files to provide desktop features such as waybar for a toolbar, and rofi for launching software.
	\item Configured and designed a Neovim configuration which I use as my primary text editor, and implemented IDE features such as code highlighting and debugging through open-source plugins.
	\item Created simple bash scripts to automate small tasks, and created configuration files for any CLI tools that I used such as tmux or zoxide.
    \end{itemize}
}

\end{document}
