\documentclass[11pt,english]{article}	

\usepackage[document]{ragged2e}

\usepackage{../../preamble}
\usepackage{../../customs}

\begin{document}

\columnratio{0.31}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}
\colseprulecolor{white}


% LEBENSLAUF HIERE
\AtBeginShipoutFirst{\Header{Cover Letter}\Footer{1}}
\AtBeginShipout{\AtBeginShipoutAddToBox{\Header{Cover Letter}\Footer{2}}}

\newpage

\colseprulecolor{lightcol}
\columnratio{0.67}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}

% \fcolorbox{white}{white}{
\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\LARGE{\textbf{\textcolor{maincol}{En-Liang (Leon) Lee}}} \\[2pt]
	\normalsize\icontext{MobilePhone}{16}{+44 7392 381253}{black}\\
	\iconemail{Envelope}{16}{enliang.leon.lee@gmail.com}{black}\\
\end{minipage}

\bigskip\bigskip

\begin{minipage}[c][3cm][b]{1\mpwidth}
	\today
	\bigskip

	Babcock International Group

	Rosyth

	Dunfermline

	Kircaldy

	KY11 2YD

	GB
\end{minipage}
\bigskip\bigskip

Dear Sir or Madam,
\medskip

I am writing to express my interest in the Software Engineering Graduate Programme. As someone with a strong background in Computer Science, I believe I have the skills to perform in this job, and I am willing to do what it takes to take my experience to the next level.

\medskip

From my degree studying at the University of Edinburgh, I have developed good discipline for balancing workloads, as well as a strong foundation to data science and programming. I have a lot of experience in Python and Jupyter Notebooks, having done courses like Software Testing and Foundation in Data Science. I also have a good knowledge of Computer Science theory, especially machine learning from courses like Foundations of Natural Language Processing and Modelling Concurrent Systems. Additionally, I also have experience in object-oriented languages like Java. As a joint major, I have also amassed a lot of mathematics experience, including work in Differential Equations and several-variable calculus which I believe provides a good basis to work in this profession.

\medskip


I have 4 years of experience working in Technical Theatre, and from working at the Edinburgh Fringe as Technical Manager of Bedlam Fringe, I have developed good interpersonal skills. I was responsible for communicating with the 23 shows performing at the theatre, which meant I was the primary contact to the companies for technical requirements, both sorting out anything in the pre-production before the festival and any issues that happened during the festival. Communication within the management team was also important for the festival to run smoothly, and I kept in good contact with the Venue Manager, Programmer, and Front of House Manager all throughout the Fringe to ensure there were no problems. 

\medskip

I hope my experience would be valuable, and thank you for looking at my application. I look forward to hearing from you.

\medskip
Sincerely,

Leon Lee.
\end{document}
