\documentclass[10pt,english]{article}	

\usepackage[document]{ragged2e}

\usepackage{../../preamble}
\usepackage{../../customs}

\begin{document}

\columnratio{0.31}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}
\colseprulecolor{white}


% LEBENSLAUF HIERE
\AtBeginShipoutFirst{\Header{Cover Letter}\Footer{1}}
\AtBeginShipout{\AtBeginShipoutAddToBox{\Header{Cover Letter}\Footer{2}}}

\newpage

\colseprulecolor{lightcol}
\columnratio{0.67}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}

% \fcolorbox{white}{white}{
\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\LARGE{\textbf{\textcolor{maincol}{En-Liang (Leon) Lee}}} \\[2pt]
	\normalsize\icontext{MobilePhone}{16}{+44 7392 381253}{black}\\
	\iconemail{Envelope}{16}{enliang.leon.lee@gmail.com}{black}\\
\end{minipage}

\bigskip

\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\today
	\bigskip

	[Hiring Manager]

	[Company Name]

	[Address]

	[Postcode]

	[City]

	[Country]
\end{minipage}
\bigskip\bigskip

Dear [Hiring Manager],
\medskip

I am writing to express my interest in [JOB]. As someone with a strong background in Theatrical Lighting Design, and a degree in Computer Science, I believe I have the skills to perform in this job.

\medskip

From my degree studying at the University of Edinburgh, I have developed good discipline for balancing workloads, as well as a strong foundation to data science and analysis. I have a lot of experience in applying data analysis in Python, and have experience in other languages like Java as well. I have also done a lot of mathematics experience including in Differential Equations and several variable calculus which I believe provides a good basis to work in this profession.

\medskip

I have 4 years of experience in technical theatre from volunteering at the Edinburgh University's student theatre society, Bedlam, and from that I have gained a strong understanding of theatrical lighting. I have designed many theatrical rigs, and have Lighting Designer of many shows. I also have experience using the CAD software Vectorworks for creating building designs for Theatre Auditoriums, and have created a scale model of the Bedlam Theatre to aide creation of lighting rigs. I believe these abilities can transfer into Exterior Lighting, and from my stem-based degree I believe I can adapt to whatever other information I would require.

\medskip

From working at the Edinburgh Fringe as Technical Manager of Bedlam Fringe, I have developed good interpersonal skills, as I was partially responsible for communication with the 23 shows performing at the theatre. I was the primary contact to the companies for technical requirements, both sorting out anything in the pre-production before the festival, and any issues that happened during the festival. Communication within the management team was also important for the festival to run smoothly, and I kept in good contact with the Venue Manager, Programmer, and Front of House Manager all throughout the Fringe to ensure there were no problems.

\medskip

I hope my experience would be valuable, and thank you for looking at my application. I look forward to hearing from you.
\medskip

Sincerely,

Leon Lee.
\end{document}
