\documentclass[../../cv-cs.tex]{subfiles}
\begin{document}

\cvevent
{04/2025 - 09/2025}
	{Technical Manager}
	{Bedlam Fringe}
	{\begin{itemize}
	    \item Liaised and co-operated with 23 companies regarding technical requirements over the 2025 Festival Fringe.
		\item Designed and led the rigging of lighting fixtures, as well as creating a simple TCP network for consoles to communicate via the OSC protocol.
		\item Team Leader to three Venue Technicians, responsible for managing the lighting and sound equipment in a 90-seat theatre over Fringe.
		\item Created and performed Project Management through the cloud-based database application Airtable.
	\end{itemize}}

	\vfill\null

\cvevent
{04/2024 - 04/2025}
	{Technical Manager}
	{Bedlam Theatre}
	{
		Volunteered at the Bedlam Theatre, working to maintain the technical equipment, and providing support to show teams performing at the venue.

		\begin{itemize}
			\item Supported student technicians working on shows, providing technical knowledge and ensuring that they work safely and realistically. 
			\item Taught the knowledge of technical equipment through workshops and beginner-friendly shows, as well as training technical crew safe practices. 
			\item Maintained the equipment in the Bedlam Theatre, including replacements for bulbs, managing cables, and any other equipment/fixture repairs. 
			\item Managed hires of equipment with any clients wanting to use the equipment in the Bedlam Theatre. 
	\end{itemize}
}
\vfill\null
%
% \cvevent
% {02/2022 - 01/2023}
% 	{High School Maths Tutor}
% 	{Edinburgh Tutors}
% 	{\begin{itemize}
% 	    \item Tutored Scottish National 5 and Higher Mathematics to pupils, both online and in-person. Led sessions once a week, and prepared my own material to lead the tutoring sessions.
% 	\end{itemize}}
%
% 	\vfill\null
%
%
\end{document}
