\documentclass[10pt,english]{article}	

\usepackage[document]{ragged2e}

\usepackage{../../preamble}
\usepackage{../../customs}

\begin{document}

\columnratio{0.31}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}
\colseprulecolor{white}


% LEBENSLAUF HIERE
\AtBeginShipoutFirst{\Header{Cover Letter}\Footer{1}}
\AtBeginShipout{\AtBeginShipoutAddToBox{\Header{Cover Letter}\Footer{2}}}

\newpage

\colseprulecolor{lightcol}
\columnratio{0.67}
\setlength{\columnsep}{2.2em}
\setlength{\columnseprule}{4pt}

% \fcolorbox{white}{white}{
\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\LARGE{\textbf{\textcolor{maincol}{En-Liang (Leon) Lee}}} \\[2pt]
	\normalsize\icontext{MobilePhone}{16}{+44 7392 381253}{black}\\
	\iconemail{Envelope}{16}{enliang.leon.lee@gmail.com}{black}\\
\end{minipage}

\bigskip

\begin{minipage}[c][2.5cm][c]{1\mpwidth}
	\today
	\bigskip

	[Hiring Manager]

	[Company Name]

	[Address]

	[Postcode]

	[City]

	[Country]
\end{minipage}
\bigskip\bigskip

Dear Sir or Madam,
\medskip

I am writing to express my interest in the role of Graduate Support Engineer. As someone with a strong background in networking from a strong background in technical theatre, and a degree in Computer Science, I believe I have the skills to perform in this job.

\medskip

From my degree studying at the University of Edinburgh, I have developed good discipline for balancing workloads, as well as a strong ability in Python from various courses in various topics such as programming compilers, natural language processing, and data science. I also have experience programming in other languages like Java. Additionally, I have a lot of mathematics experience including in Differential Equations and several variable calculus which I believe provides a good basis to work in this field.

I have a lot of experience using git to manage my personal files, including the notes for all of my courses which I have written using LaTeX. I also have experience in test cycles from taking a course in Software Testing where we used CI/CD Pipelines through Github Actions, Jest, and Postman to automate the testing process of a simple JavaScript API.

\medskip

I have 4 years of experience in technical theatre from volunteering at the Edinburgh University's student theatre society, Bedlam. From this, I have developed a strong understanding of networking from sending digital audio signals via the DANTE protocol, and I have achieved DANTE Level 2 training which has given me a lot of information on networking including managing switches, and management of Subnets and VLANs. I also have a lot of experience using the OSC protocol, which lets theatrical consoles communicate with each other, as well as experience using sACN which is a Lighting protocol for transmitting DMX-512 data. I believe these abilities can transfer into networking in Calnex, and I believe I have the ability to learn any new information I would need.
\medskip

From working at the Edinburgh Fringe as Technical Manager of Bedlam Fringe, I have developed good interpersonal skills, as I was partially responsible for communication with the 23 shows performing at the theatre. I was the primary contact to the companies for technical requirements, both sorting out anything in the pre-production before the festival, and any issues that happened during the festival. Communication within the management team was also important for the festival to run smoothly, and I kept in good contact with the Venue Manager, Programmer, and Front of House Manager all throughout the Fringe to ensure there were no problems.

\medskip

I hope my experience would be valuable, and thank you for looking at my application. I look forward to hearing from you.
\medskip

Sincerely,

Leon Lee.
\end{document}
